\textbf{Senior Data Engineer} \hfill Al-Rajhi Bank \{ARB\}, Riyadh, Saudi Arabia \\
\textit{January 2025 – Present}
\begin{itemize}
    \item Developed and optimized ETL mappings, workflows, and applications in DEV, SIT, and UAT using Informatica DEI and Informatica Developer Tool.
    \item Integrated multiple data sources: MSSQL, Oracle, flat files, and Kafka streaming events.
    \item Contributed to High-Level and Low-Level Design (HLD/LLD) documentation.
    \item Actively worked within Agile frameworks using JIRA and Confluence, regularly reporting progress and closing tickets.
    \item Updated and maintained data models using ERwin Data Modeler to reflect business and technical changes.
    \item Designed and deployed a centralized ELK stack (Elasticsearch, Logstash, Kibana) for monitoring Informatica DEI.
    \item Built and customized Kibana dashboards to visualize system health, application performance, and error trends—improving incident detection and resolution.
    \item Developed a chat bot using Retrieval-Augmented Generation (RAG) technology to summarize design documents.
\end{itemize}

\textbf{Data Engineer} \hfill Credit Agricole Egypt, Cairo, Egypt \\
\textit{December 2023 – December 2024}
\begin{itemize}
    \item  Converted legacy PL/SQL procedures into Informatica PowerCenter mappings and workflows.
    \item  Developed, and tested ETL mappings to consolidate financial data and enhance data accuracy.
    \item  Participated in SIT, UAT, and deployment phases to resolve issues and ensure data integrity across all ETL environments.
    \item  Optimized SQL queries and PL/SQL code to improve performance and reduce execution
\end{itemize}

\textbf{Data Engineer} \hfill Banque Misr, Cairo, Egypt \\
\textit{June 2022 – March 2023}
\begin{itemize}
    \item Developed and tested OFSAA Funds Transfer Pricing \(FTP\) methods and cost allocation rules \(PFT\).
    \item Developed, and tested ETL mappings to consolidate financial data and enhance data accuracy.
    \item Participated in SIT, UAT, and deployment phases to resolve issues and ensure data integrity across all ETL 
environments.
\end{itemize}

\textbf{Jonir Data Engineer} \hfill Credit Agricole Egypt, Cairo, Egypt \\
\textit{August 2021– June 2022}
\begin{itemize}
    \item Developed ETL pipelines using T2T and SCD tools in OFSAA\%
    \item Built and optimized multiple ETL maps using Informatica PowerCenter to drive OFSAA data warehouse.
    \item Developed, Tested and integrated custom PL/SQL packages, procedures, functions, and triggers to support ETL processes.
    \item Optimized SQL queries and PL/SQL code to improve performance and reduce execution time.
\end{itemize}
