Senior Data Engineer with 5+ years of experience building cloud-native data platforms and data products supporting analytics, reporting, and product decision-making. Specialized in scalable ELT pipelines, semantic data modeling, real-time ingestion, and enabling self-serve analytics in high-growth fintech and regulated banking environments.
\begin{itemize}
    \item Experienced in replacing legacy enterprise systems with scalable lakehouse architectures
    \item enabling low-latency analytics, real-time ingestion, and governed data delivery.
\end{itemize}

\begin{verse}
    
    \subsection{Proof of Impact}
    \begin{itemize}
        \item Led the migration from a legacy data warehouse to a modern cloud-native lakehouse, enabling analytics engineering workflows, faster experimentation, and consistent metric definitions across product and business teams.
        \item Designed and implemented a real-time data ingestion pipeline that improved data freshness by 60\%, enabling faster decision-making for business stakeholders.
        \item Designed real-time integration between multiple systems reducing the number of API calls by 70\% and improving system reliability.    
    \end{itemize}
    \subsection{Business outcomes delivered}
    \begin{itemize}
        \item Reduced data processing time by 40\% and operational costs by 25\% through modernizing the data platform.
        \item Improved data freshness by 60\% with a real-time ingestion pipeline, enabling faster decision-making.
        \item Decreased API calls by 70\% and enhanced system reliability through integrated real-time data flows.
    \end{itemize}
\end{verse}